\textsf{Are large language models superhuman chemists?}

### 2024-10-06 src/tex/appendix.tex
feat: add corpus table

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_score_distribution.pdf}
    \script{plot_human_score_distribution.py}
    \label{fig:human_score_distribution}
    \caption{\textbf{Distribution of human scores.} The histogram and kernel density estimates show the fraction of questions answered completely correctly.
    Since the best possible score for each question is one and the worst possible score is zero, the values on this plot are between zero and one.}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_timing.pdf}
    \script{analyze_human_data.py}
    \label{fig:human_timing}
    \caption{\textbf{Time taken by human scorers to answer questions vs.\ correctness of their answers.} From the plot, it is clear that there is no clear dependence of the correctness of the answers on the time taken by the human scorers to answer the questions.}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/experience_vs_correctness.pdf}
    \script{analyze_human_data.py}
    \label{fig:experience_vs_correctness}
    \caption{\textbf{Experience of human  scorers vs.\ correctness of their answers.} The experience (in the number of years since the first university-level chemistry course) of the human scorers was not significantly correlated with the correctness of their answers.}
\end{figure}

>>>>

The corpus of the questions in Chembench, as shown in \Cref{tab:chembench_corpus}, can be divided according to which topic they belong, or which type of knowledge is required in order to solve them correctly.

\begin{table*}[!t]
    \centering
        \caption{Summary of ChemBench question types.
    }
    \begin{tabular}{p{2.7cm}cp{10cm}}
        \toprule
        \textbf{Question Type} & \textbf{\%} & \textbf{Example Questions}  \\ 
        \midrule
        Chemical Preference & 35.0 & Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
        & & A. [START_SMILES]N#Cc1ccc(OCCCN2CC3CN(CCNS(=O)(=O)c4ccc(F)cc4)CC(C2)O3)cc1[END_SMILES] \\
        & & B. [START_SMILES]O=C1CC(c2ccc(CC(NS(=O)(=O)c3cc(Cl)cc(Cl)c3)c3nc4ccccc4[nH]3)cc2)S(=O)(=O)N1[END_SMILES] \\
        \midrule
        Technical Chemistry & 1.5 & Which of the following statements is true about the different types of ideal reactors? \\
        & & A. In a batch reactor, the composition is uniformly mixed and remains the same throughout the reactor and at the exit \\
        & & B. In a batch reactor, the fluid passes through the reactor with no mixing of earlier and later entering fluid \\
        & & C. In a mixed flow reactor, the composition changes with time but is uniform everywhere within the reactor \\
        & & D. In a plug flow reactor, the fluid moves in single flow through the reactor with no mixing and no overtaking \\
        \midrule
        Organic Chemistry & 15.5 & What is the reaction mechanism that describes the following reaction (represented using reaction SMILES) [START_RXNSMILES]CCCl.CO[Na]>>[Na]Cl.CCOC[END_RXNSMILES]? \\
        & & A. $E_1$ \\
        & & B. $E_{cb}$ \\
        & & C. $S_N1$ \\
        & & D. $S_N2$ \\
        \midrule
        Toxicity/Safety & 24.2 & What details pertaining to a hazardous substance can be located on a Material Safety Data Sheet (MSDS)? \\
        & & A. All hazards regarding the material \\
        & & B. Physical and chemical properties \\
        & & C. Precautions for safe handling and storage \\
        \midrule
        Analytical Chemistry & 5.8 & Which of the following analytical methods is most appropriate for performing a survey analysis of a solid sample containing various metals? \\
        & & A. X-ray fluorescence analysis \\
        & & B. Differential pulse polarography \\
        & & C. Flame-atomic absorption spectroscopy \\
        & & D. Gas chromatography with flame ionization detector \\
        & & E. Hydride generation atomic absorption spectroscopy \\
        \midrule
        Materials Science & 3.1 & For NMR analysis, you need to digest the MOF in a strong acid to remove the linker and leave the metal clusters intact. Why would one choose \\ce{HF} over \\ce{HCl} for this purpose? \\
        & & A. \\ce{F-} forms a stable bonds to the metal ions \\
        & & B. \\ce{HF} has a better water solubility than \\ce{HCl} \\
        & & C. \\ce{HF} has a higher boiling point than \\ce{HCl} \\
        & & D. \\ce{HF} is a weaker acid than \\ce{HCl} \\
        \midrule
        General Chemistry & 5.3 & Which of the following salts is an acidic salt? \\
        & & A. \\ce{NH4Cl} \\
        & & B. \\ce{Na2CO3} \\
        & & C. \\ce{NaH2PO4} \\
        & & D. \\ce{Zn(OH)Cl} \\
        \midrule
        Physical Chemistry & 6.3 & The Born-Oppenheimer (BO) approximation is widely used in computational chemistry, but its accuracy can vary depending on the system. Among the following options, for which system is the Born-Oppenheimer approximation likely to be least applicable? \\
        & & A. \\ce{C60} \\
        & & B. \\ce{CH4} \\
        & & C. \\ce{Fe(CO)5} \\
        & & D. \\ce{H2+} \\
        & & E. \\ce{NaCl} \\
        \midrule
        Inorganic Chemistry & 3.3 & What is the oxidation number of the metal in the compound \\ce{[ZrF7]^{3-}}\\
        \toprule
        \textbf{Reasoning Type} & \textbf{Number of Questions} & \textbf{Example Question} \\
        \midrule
        Knowledge & 770 & Which of the following salts is an acidic salt? \\
        & & A. \\
        \midrule
        Reasoning & 825 & How can the optical impact of quantum confinement on the electronic structure of a quantum dot be observed experimentally? \\
        & & A. By measuring atomic force microscopy \\
        & & B. By measuring fourier transform infrared spectroscopy \\
        & & C. By measuring photoluminescence spectrum \\
        & & D. By measuring the absorption spectroscopy \\
        \midrule
        Intuition & 1001 & Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
        & & A. [START_SMILES]CC1(C)Oc2ccc([N+](=O)[O-])cc2[C@@H](N2CCOCC2)[C@@H]1O[END_SMILES] \\
        & & B. [START_SMILES]Cc1ccccc1N=C(S)N1CCC(NC(=O)c2ccco2)CC1[END_SMILES] \\
        \midrule
        Calculation & 91 & Given that the average molar mass of the polymer chains in this sample of poly(lactic acid) (PLA) is \\pu{595 g mol^{-1}} using end-group analysis, where \\pu{0.1619 g} of PLA was dissolved in \\pu{25 cm^3} of benzyl alcohol and titrated with \\pu{0.0400 mol dm^{-3}} \\ce{KOH} solution. The volume of \\ce{KOH} solution required to reach the endpoint was \\pu{6.81 cm^3}. What is the average number of monomer units in each polymer chain of this sample? \\
        \bottomrule
    \end{tabular}
    \label{tab:chembench_corpus}
\end{table*}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_score_distribution.pdf}
    \script{plot_human_score_distribution.py}
    \caption{\textbf{Distribution of human scores.} The histogram and kernel density estimates show the fraction of questions answered completely correctly.
    Since the best possible score for each question is one and the worst possible score is zero, the values on this plot are between zero and one.}
    \label{fig:human_score_distribution}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_timing.pdf}
    \script{analyze_human_data.py}
    \caption{\textbf{Time taken by human scorers to answer questions vs.\ correctness of their answers.} From the plot, it is clear that there is no clear dependence of the correctness of the answers on the time taken by the human scorers to answer the questions.}
    \label{fig:human_timing}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/experience_vs_correctness.pdf}
    \script{analyze_human_data.py}
    \caption{\textbf{Experience of human  scorers vs.\ correctness of their answers.} The experience (in the number of years since the first university-level chemistry course) of the human scorers was not significantly correlated with the correctness of their answers.}
    \label{fig:experience_vs_correctness}
\end{figure}
